
\chapter*{Acknowledgments}
\markboth{}{}
Looking back at the journey to pursue my PhD, I realize that many things happened in only four years and that this thesis would have never seen the light without the support of many people who I would like to thank here.  

First and foremost, my gratitude goes to my supervisors for leading me during this path. I would never be able to write this thesis without their help.

Wilbert, thank you for your constant support and patience. Every meeting and discussion with you contributed to this work and to my professional growth. 
You have listened all my doubt and replied to my questions at any time of the day.
I learned a lot from you and I am impressed about the breadth of your knowledge and the passion you have for your work. 

Jan, thanks for being extremely available and for your daily encouragement. The door of your office was always open for any advice. 
I really appreciated your meticulousness in correcting the text of my papers and of this thesis, they helped me a lot to improve my writing skills.

I am thankful to Teus Tukker who was one of my supervisors during the first year of my PhD. It is a pity you have taken part of this project only for a short time, your guidance had a big impact to me.

I would like to express my gratitude to all the members of my doctorate committee for having agreed to referee my thesis and for their fruitful comments.  

I would extend my appreciation to Jorg for providing me his master thesis from which this work starts and for the time he dedicated me for further explanations.

I wish to thanks Carlo you for the helpful discussions about Chapter \ref{chap:raytracing} and for the cover of my thesis. 

Carla, Guido, Michele e Giacomo, thank you for your suggestions for the final decision of the cover.

My first approach with the Netherlands wasn't easy at all. As many international people, especially Italians, I was complaining about food, coffee, weather and, most of all, about bikes. 
I wouldn't be able to deeply enjoy the beauty of this country if I wouldn't meet great friends and colleagues.

I am indebted with all the CASA members for creating a nice and international work atmosphere. This would never be possible without the help of Enna, Marese and Jolijn who organized very nice events within CASA group. Thanks Enna for helping me with the university bureaucracy.

I also found a cozy working environment in Philips Lighting. I thanks all the people working there for bringing enthusiasm every day, I really enjoyed the international cooking events. Especially, I thanks Andrea for her help and availability.

Thanks to my current and former officemates: Nitin, Thomas, Mohammad, Harshit, Behnaz, Deepesh, Yuri and Pranav for helping me to keep the concentration every day.
In particular, thanks to Deepesh and Behnaz for having supported me and for the nice and pleasure time we spent together. I will be always grateful of your friendship. 

Laura, thank you for your cute and encouragement words during my stressful time of writing the thesis.

Giovanni and Deepesh thanks for hosting me at your place when I wasn't able to walk. I will never forget the kindness and thoughtfulness you had for me.


Letizia, Gonzalo and Giovannino thank you for walking with me very slowly around the city and for finding the time to have a chat together. Thanks Letizia for making your car always available to pick me up.

Carla for organizing me a great birthday party and for cooking delicious Italian dishes for all of the people there.

During these years I also had the opportunity to join the "Kabelstraat" events. I am thankful to all the people there for the funny evenings and good dinners together.

I wish to thanks my friends and former colleagues back in Italy: Federica, Ida, Stefania, Daniela and Arianna. It was nice to study with you at the university and it looks amazing to me that after years we are still in touch.

Misa, Ale G., Ghislaine, Chiara, Manouk, Tsvetan and Jacopo, I will never regret to have shared our house with you. Thanks for never making me feel lonely coming back home after work. I discovered the beauty and the difficulty to meet up with people of different cultures.

During these years I discovered a concentration of Italians at the fourth floor of our department. Thanks Ale G., Ale Z., Carlo, Enrico, Fabio, Lorenzo, Marta and Misa for making me feel like home. I will miss our barbecue parties in Tongelresestraat.

Before starting my PhD, I would never thought to start doing climbing in a flat country. This sport had the powerful to make my mind rested after long days in the office.
I would like to thank all my climbing friends for having motivated me and for sharing with me their passion. Most of all, Ale Z. for being my personal climber teacher, and Carlo for making me discover how wonderful is to climb on the real rock. 

A special thank goes to my family, especially to my parents and my sister.

Dad, you have been always a mystery for me. I am not able to explain all my emotions for you, but I can say for sure that the strongest feelings I have for you are love and endearment. Thank you for all what you did for our family. I like thinking you have been at my side for all these years, and that now you are proud of me.

My mother for her support. Mamma, grazie per avermi supportato in ogni momento e non aver mai ostacolato le mie scelte nonostante a volte abbiano causato sofferenza e nostalgia per la distanza che ci separa. Il tuo amore e la tua fiducia in me, sono stati fondamentali per il raggiungimento di questo traguardo. Ti voglio bene.   

My sister Carla for having been part of my \textit{entire} life. Sister, I cannot put into words how grateful I am, and how much I owe you. You are my strength and my point of reference. I would never be able to pursue none of my successes without you.
I miss sharing the daily life with you but I feel so lucky when I realize that the distance did change nothing. 

I desire to thank Guido for having organized very beautiful excursions around the south of Germany and the nice time we spent in the Netherlands with Carla and Carlo. I have a good memory of all the trips we made together. You are a nice and warm-hearthed person.

Last, but not least, I wish to thank you, Carlo, for your love and for bringing color and brightness in my life.
Thanks for letting me be at your side and for your way to stand by me. I cannot imagine my future without you.
%\clearpage{\pagestyle{empty}\cleardoublepage}
\addcontentsline{toc}{chapter}{Acknowledgments}